%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{ragged2e} % for \justifying
\usepackage{microtype} % better justification




%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} \& Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} \& Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Gerard Consuelo} \\ \vspace{1pt}
    {San Jose, CA, 95112} $|$ 
    {(279)-220-0586} $|$ 
    \href{mailto:gcon.work@gmail.com}{\underline{gcon.work@gmail.com}} $|$ 
    \href{https://linkedin.com/in/gerard-consuelo}{\underline{linkedin.com/in/gerard-consuelo}} $|$
    \href{https://github.com/epicgdog}{\underline{github.com/epicgdog}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {San Jose State University}{San Jose, CA}
      {Bachelor of Science in Computer Science}{Graduation: 2027}
       \resumeItemListStart
        \resumeItem{GPA: 4.0 (President's Scholar Award).}
        \resumeItem{Coursework: Data Structures \& Algorithms, Linear Algebra, Operating Systems, Network Security.}
        \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
  {Peer Mentor}{Aug. 2025 -- Present}
  {SJSU Peer Connections}{San Jose, CA}
  \resumeItemListStart
    \resumeItem{Partnered with university faculty to co-facilitate MATH 30W, decreasing course failure rates by 25\%.}
    \resumeItem{Designed and facilitated a 5-week workshop program for of 30+ students, receiving over 95\% positive feedback.}
    \resumeItem{Distilled complex Calculus I concepts into intuitive frameworks during 1-on-1 sessions, helping 30+ students pass.}
    \resumeItem{Coordinated logistics by managing schedules, generating progress reports, and maintaining a professional tone.}
  \resumeItemListEnd

  
  \resumeSubheading
  {Software Engineer Intern}{May 2025 -- Aug. 2025}
  {SJSU College of Engineering}{San Jose, CA}

  \resumeItemListStart
    \resumeItem{Engineered \& deployed a print tracking system serving 2,000+ members, processing 10+ daily jobs with 99.9\% uptime.}
    \resumeItem{Implemented REST APIs to send files to printer using Line Printer Daemon protocol, Python, \& FastAPI.}
    \resumeItem{Monitored print‑job status via lpstat; persisted job IDs \& states in SQLite for auditability \& reporting.}
    \resumeItem{Built a status dashboard to relay print‑job info using React.js \& Tailwind CSS, served efficiently with Nginx.}
    \resumeItem{Created a pytest suite for FastAPI endpoints, LPD submission, \& lpstat/SNMP parsing with robust mocks.}
  \resumeItemListEnd
  
    
  \resumeSubheading
  {Summer Camp Lead}{Jul. 2025}
  {theCoderSchool}{Folsom, CA}
  \resumeItemListStart
    \resumeItem{Directed an intensive Roblox game development camp for 15+ students where 95\% deployed playable prototypes.}
    \resumeItem{Developed 5+ mini-games in LuaU \& 7 lessons on scripting, events, \& OOP fundamentals designed for 8-12 year olds.}
    \resumeItem{Designed \& executed a curriculum that drove student comprehension scores from 56\% to 84\%}  
  \resumeItemListEnd

  \resumeSubheading
  {Game Developer}{Jan. 2023 -- Aug. 2023}
  {Roblox}{Remote}
  \resumeItemListStart
    \resumeItem{Engineered a FPS framework in LuaU adhering to MVC \& OOP principles, educing code redundancy by 30\%.}
    \resumeItem{Implemented robust Datastores with automated saving \& error handling, ensuring 100\% data persistence.}
    \resumeItem{Architected a high-concurrency NPC system using A* pathfinding \& FSMs, sustaining 300+ agents <15ms.}
    \resumeItem{Designed \& created production-ready 3D assets \& animations in Blender.}
  \resumeItemListEnd
        
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch \& streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
    
\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

    \resumeProjectHeading
        {\textbf{\href{https://github.com/Javacadu/HotSpotHackDavis25}{HotSpot}} $|$ \emph{Next.js, React, Tailwind CSS, Mapbox GL JS, Google Gemini}}{}
        \resumeItemListStart
          \resumeItem{Real-time disaster aid platform aggregating California wildfire data, updating resources/status every 2 minutes.}
          \resumeItem{Created a geospatial map application using Next.js, React, Tailwind CSS, Mapbox GL JS with live data from NASA.}
          \resumeItem{Integrated Google Gemini with Census data to curate the necessary resources based on the demographics affected.}
      \resumeItemListEnd

    %   \resumeProjectHeading
    %     {\textbf{\href{https://github.com/DanielYRoh/syllabus-scraper}{Syll.Ai}} $|$ \emph{Next.js, React, Tailwind CSS, Vercel, Supabase, FastAPI, ngrok, Google Gemini}}{}
    %       \resumeItemListStart
    %     \resumeItem{Generated structured study cards from syllabi, cutting student preparation time by 75\% across pilot users.}
    %     \resumeItem{Implemented a full-stack application, powered by Next.js, Tailwind CSS, Vercel, Supabase, \& ngrok.}
    %     \resumeItem{Leveraged a FastAPI backend integrated with Google Gemini to extract \& curate key information.}
    % \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Schedule Builder AI} $|$ \emph{Next.js, Python (FastAPI), PostgreSQL, Pinecone, Celery, LangChain}}{}
          \resumeItemListStart
            \resumeItem{Hybrid Scheduling Engine combining an scheduling algorithm with a RAG-based AI agent for personalized class schedules.}
            \resumeItem{Architected an async data pipeline using Celery, hydrating a PostgreSQL database with real-time course data.}
            \resumeItem{Implemented a Vector Search system to index "Rate My Professor" reviews, utilizing a custom MCP server.}
            \resumeItem{Designed an Entity Resolution layer to normalize inconsistent data sources, ensuring 100\% data integrity.}
    \resumeItemListEnd


    
\resumeSubHeadingListEnd

    \section{Technical Skills}
     \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
         \textbf{Languages}{: LuaU, Python, Java, C, HTML/CSS, JavaScript, SQL} \\
         \textbf{Frameworks}{: Node.js, Next.js, React, Express, FastAPI, Tailwind CSS, RobloxAPI} \\
         \textbf{Developer Tools}{: Git/Github, Docker, VS Code, Linux, Vercel, PostgreSQL, Pinecone, Celery, LangChain} \\
        }}
     \end{itemize}
\end{document}