%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Gerard Consuelo} \\ \vspace{1pt}
     \href{mailto:gcon.work@gmail.com}{\underline{gcon.work@gmail.com}} $|$ 
    \href{https://linkedin.com/in/gerard-consuelo}{\underline{linkedin.com/in/gerard-consuelo}} $|$
    \href{https://github.com/epicgdog}{\underline{github.com/epicgdog}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {San Jose State University}{San Jose, CA}
      {Bachelor of Arts in Computer Science}{Aug. 2024 -- Present}
       \resumeItemListStart
        \resumeItem{GPA: 3.95/4.0 (President's Scholar Award)}
        \resumeItem{Relevant Coursework: Intro to Data Structures, Linear Algebra, Discrete Mathematics}
        \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

     \resumeSubheading
      {Software Engineer Intern @ SCE}{Sep 2024 -- Present}
      {San Jose State University}{San Jose, CA}
      \resumeItemListStart
        \resumeItem{Designed, developed, and tested a self-checkout system for snacks serving a club of over 100 students.}
        \resumeItem{Implemented a REST API to perform CRUD operations in Golang using Gin synced with a SQLite database, enabling seamless inventory management.}
        \resumeItem{Secured endpoints with JWT tokens for user authentication, allowing for exclusive admin editing access. }
         \resumeItem{Containerized with Docker, allowing other developers access across multiple networks.   }
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Academic Tutor}{Sep. 2023 -- April 2024}
      {Folsom High School}{Folsom, CA}
      \resumeItemListStart
        \resumeItem{Coordinated weekly sessions for algebra and physics for several students ranging from middle to high school.}
        \resumeItem{Elevated C-grade students to A-level performance through personalized teaching methods tailored to individual learning styles. }
        \resumeItemListEnd
    
\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Syll.ai @ SFHacks} | \href{https://github.com/DanielYRoh/syllabus-scraper}
          {\underline{Frontend}
          }
          \href{https://github.com/darrensh3n/pdf-scraper-api}
          {\underline{Backend}
          }
          
          }{April 2025}
          \resumeItemListStart
        \resumeItem{Collaborated to develop a syllabus scraping tool that extracted key academic information and transformed it into digestible digital cards, reducing student time spent on manual review by 75\%.}
        \resumeItem{Implemented a backend service with FastAPI that converted syllabus PDFs to text for processing by Google Gemini, enabling automated data scraping and extraction.}
        \resumeItem{Engineered a high-performing, responsive web application levaraging Next.js, TailwindCSS, and Supabase to display and manage user-generated syllabus cards, incorporating robust user authentication for privacy and personalized content storage.}
    \resumeItemListEnd
    
    \resumeProjectHeading
{\textbf{Focus App} | \href{https://github.com/epicgdog/focus-app}
          {\underline{Github}
          }}{July 2023 -- August 2023}
\resumeItemListStart
\resumeItem{Developed a cross-platform desktop application with ElectronJS, React, and Node.js to implement the Pomodoro technique, boosting user productivity by 30\%\textbf{.}}
\resumeItem{Implemented a customizable timer with dynamic break/work intervals, alongside an integrated todo list and media playlist, leveraging React Hooks and state management to streamline task and song management.}
\resumeItem{Engineered a highly customizable user interface with dynamic CSS styling and a robust file I/O system for efficiently saving and retrieving user preferences. }
\resumeItemListEnd

    \resumeProjectHeading
          {\textbf{Blocky Heroes} | \href{https://www.roblox.com/games/12103017573/Game-1-Blocky-Heroes-V0-0-1}
          {\underline{Game Link}}
          }{Jan 2023 -- Feb 2023}
          \resumeItemListStart
          \resumeItem{Built a First-Person Shooter (FPS) game using the Roblox Game Engine and API, programmed in LuaU.}
          \resumeItem{Integrated a Model-View-Controller (MVC) architecture and various OOP paradigms(polymorphism, encapsulation, inheritance), which streamlined development, enhanced modularity, and facilitated testing within a rapid 2-week timeframe.}
          \resumeItem{Architected an advanced NPC system featuring a finite state machine and A* pathfinding, capable of generating 100+ NPCs concurrently with minimal latency.}
\resumeSubHeadingListEnd

    \section{Technical Skills}
     \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
         \textbf{Languages}{: Java, JavaScript, LuaU, HTML/CSS, Python, Golang} \\
         \textbf{Frameworks}{: NextJS, ElectronJS, React, Express, Node.js, FastAPI, TailwindCSS, RobloxAPI, SciKit, Pandas} \\
         \textbf{Developer Tools}{:Git, Github, Docker, VS Code, WSL} \\
        }}
     \end{itemize}
\end{document}